How does color influence our political conversations?

### 2023-07-09 chapter_3/src/slides/slides.qmd
add ISPP slides

::: {.notes}
- This is a chapter from a larger book project.
- The book addresses the question: 
  - does color convey political information? 
  - does it have pre-conscious effects on information that comes later?
:::

@@

# Sensitivity of conclusions to sample size, research design, and modeling strategies

>>>>

::: {.notes}
- This is a chapter from a larger book project.
- The book addresses the question: 
  - does color convey political information? 
  - does it have pre-conscious effects on information that comes later?
- The goal here is to start off by building up some exepectations in simple cases with a psychological model. Other complications are certainly interesting and will be saved for future projects. For now, want to start simple.
:::

@@

# Sensitivity of conclusions to sample size, research design, and modeling strategies {.appendix}
